### 2022-07-02 paper/main.tex
more bnrw

@@

% REFS:
% https://books.google.com/books?id=BmwuDwAAQBAJ&lpg=PP1&ots=_PlVBghHER&dq=media%20and%20crime&lr&pg=PP1#v=onepage&q=media%20and%20crime&f=false
% https://doi.org/10.1177/0002716295539001011
% https://doi.org/10.1177/0002764296039004003
% https://doi.org/10.1177/19401612211020929
% https://www.cambridge.org/core/books/television-and-its-viewers/83C017F8F8416B5D5F2716EBE5D354BF
% http://personal.psu.edu/exs44/597b-Comm&Crime/Wilson-Kelling-Broken%20Windows.pdf
% https://researchgate.net/profile/Tracey-Meares-2/publication/268224149_The_Law_and_Social_Science_of_Stop_and_Frisk/links/54665ea60cf25b85d17f6112/The-Law-and-Social-Science-of-Stop-and-Frisk.pdf
% https://oxford.universitypressscholarship.com/view/10.1093/acprof:oso/9780195369083.001.0001/acprof-9780195369083

@@

@@

\par TODO: what reddit is and its role in misinformation. crime and social media papers

\par Reddit citation test \cite{ftahmsabi}

@@

\subsection{Reddit Data}
\par The Reddit dataset contains posts from the subreddits of the 384 MSAs of the United States as of March 2020 \cite{censusmetro}. From this list of subreddits, we scrape and store all posts that users submit. In total, 161,166 posts were gathered between April 5, 2022 and May 31, 2022. A timeline of this process can be seen in Figure \ref{fig:line-1}. The datastore archives posts in two formats. First, posts are written to a system of record to ensure that there is an authoritative data source that can be referenced. Second, pertinent information, such as post title and author, is extracted from the posts data stream and placed in a separate datastore.

>>>>

\subsection{Geography and the Internet}

% TODO

@@

% REFS:
% https://books.google.com/books?id=BmwuDwAAQBAJ&lpg=PP1&ots=_PlVBghHER&dq=media%20and%20crime&lr&pg=PP1#v=onepage&q=media%20and%20crime&f=false
% https://doi.org/10.1177/0002716295539001011
% https://doi.org/10.1177/0002764296039004003
% https://doi.org/10.1177/19401612211020929
% https://www.cambridge.org/core/books/television-and-its-viewers/83C017F8F8416B5D5F2716EBE5D354BF
% http://personal.psu.edu/exs44/597b-Comm&Crime/Wilson-Kelling-Broken%20Windows.pdf
% https://researchgate.net/profile/Tracey-Meares-2/publication/268224149_The_Law_and_Social_Science_of_Stop_and_Frisk/links/54665ea60cf25b85d17f6112/The-Law-and-Social-Science-of-Stop-and-Frisk.pdf
% https://oxford.universitypressscholarship.com/view/10.1093/acprof:oso/9780195369083.001.0001/acprof-9780195369083
% https://policycommons.net/artifacts/1817184/news-consumption-across-social-media-in-2021/2554124/
% https://papers.ssrn.com/sol3/papers.cfm?abstract_id=2771080

@@

\par While the relationship between traditional media and crime has been thoroughly researched, the relationship between social media and crime has not been as rigorously explored. Social media, which originally started as a method of connecting with friends and family, has grown and evolved beyond its humble beginnings. Social media sites, such as Twitter, are now significant sources of new for many Americans (REF - LR: What is twitter?). (REF 9) found that nearly half of Americans consume their news from social media sites like Twitter, Facebook, and Reddit. This trend coincides with the decline of traditional media. Printed media, such as newspapers and magazines, as well as televised media, has consistently declined since the explosive growth of the Internet (REF 10). Despite this, research on social media remains sparse.

% Paragraph about relevant paper

(REF) detail the ecosystem of crime discussion on Twitter. Specifically, they look at how often crime discussion appears in Tweets posted from users in Latin American countries. Using Twitter's geolocation tags, Tweets are subdivided down to the municipality that the original user posted from. From here, the authors compared Twitter crime discussion rates to city-level documented crime rates. They did not find a correlation between high frequencies of crime-related Tweets and high rates of reported crime. The authors conclude that the Tweets do not accurately represent actual rates of crime, but they effectively capture the worry of crime in a community.

% Paragraph about misinformation

(REF) introduce an interesting observation: some of the crime-related Tweets are highly sensationalized or completely untrue. In this way, social media differs from traditional media. Traditional media acts as a gatekeeper (REF 2), where only select stories and viewpoints emerge and some degree of factchecking generally exists (REF ?). Social media, on the other hand, allows for a more diverse set of viewpoints and opinions. However, as there is generally a limited amount of moderation (REF ?) on social media platforms, blatantly false stories can spread across sites (REF). This proliferation of misinformation has become increasingly impactful in the United States. It has affected important events in recent American history, including presidential elections (REF ?) and the the response to the Covid-19 pandemic (REF ?). Despite attempts to curb the spread of misinformation on social media (REF ?), falsehoods and panics continue to spread across the web.

@@

% R1: https://arxiv.org/pdf/2010.10397.pdf
% R2: https://wapo.st/2Xvbvae
% R3: https://arxiv.org/abs/1804.07354
% R4: https://dl.acm.org/doi/abs/10.1145/3134666
% R5: https://ojs.aaai.org/index.php/ICWSM/article/view/18053
% R6: https://datacompass.lshtm.ac.uk/id/eprint/2982/
% R7: https://social.techjunkie.com/demographics-reddit (REDDIT DEMOGRAPHICS)
% R8: https://dl.acm.org/doi/pdf/10.1145/3512901
% R9: http://fsnagle.org/papers/potts2013reddit.pdf

\par While Facebook (REF ?) and Twitter (REF ?) face much of the backlash from outrage directed towards online misinformation, smaller websites, like Reddit, play a role in the distribution of sensationalized stories and misinformation as well. Reddit communities, also known as subreddits, allow users to post self-made content or link content from other parts of the web. Subreddits are dedicated to a certain topic, such as fishing, political groups, or real-life communities. Subreddits can be created by anyone and are run by volunteer moderators. As moderators are a varied group of individuals, they represent a diverse set of viewpoints not beholden to any set of limits. In this way, misinformation can seep into communities, as there are differing levels of moderation among subreddits. To combat rouge communities and moderators, Reddit has moved to ban certain subreddits that consistently break rules (REF R1).

\par Several Reddit communities have been the subject of studies on misinformation. One such subreddit is known as \texttt{The\_Donald} (TD). TD, which acted as the support community for former President Donald Trump, spread unsubstantiated conspiracy theories, such as Pizzagate (REF R2) and engaged in harassment of other communities on the website (REF - extracting inter...). TD was eventually quarantined and banned from the site, leading users to create their own Reddit offshoot website (REF R1). However, TD spread misinformation with little intervention for the nearly five years that it survived on the site (REF R1). This is largely because Reddit generally avoids intervening in communities, while occasionally banning subreddits with egregious behavior (REF R3). Several Reddit communities, including \texttt{Incels} (REF R5), \texttt{FatPeopleHate} (REF R4), and \texttt{NoNewNormal} (REF R6) that produce hateful, harassing, or misleading content, have also been banned after significant backlash.

\par Reddit has also been responsible for sensationalizing crime. In one notable example, Reddit users attempted to solve the identity of the 2013 Boston Marathon Bombers (REF R9). Reddit users believed that through community effort and brainstorming, the Reddit community could catch the killers quicker than the authorities. After the users performed their investigation, they believed that they had correctly identified the suspect and engaged in harassment of those related to him (REF R9). Ultimately, the Reddit users had identified the incorrect perpetrator. An embarrassing moment to many Reddit users, the incident nonetheless is important in showing how the fear of crime, and how social media platforms perpetrate this fear, can help radicalize individuals (REF).

@@

\subsection{Reddit Data}
\par The Reddit dataset contains posts from the subreddits of the principal cities of the 384 MSAs of the United States as of March 2020 \cite{censusmetro}. From this list of subreddits, we scrape and store all posts that users submit. In total, 161,166 posts were gathered between April 5, 2022 and May 31, 2022. A timeline of this process can be seen in Figure \ref{fig:line-1}. The datastore archives posts in two formats. First, posts are written to a system of record to ensure that there is an authoritative data source that can be referenced. Second, pertinent information, such as post title and author, is extracted from the posts data stream and placed in a separate datastore.
